### 2020-10-14 fig/pgv-scheduler.tex
Changed drawing of scheduler.

    \draw
    (agent1) -- node[pos=0.35,above] {$c_1$}
    node[pos=1.0,above] {$c'_1$} ++ (agent2);
    \draw
    (agent2) -- node[pos=0.1,above] {$c_2$}
    node[pos=0.9,above] {$c'_2$} ++ (agent3);
    \draw
    (agent3) -- node[pos=0.0,above] {$c_3$}
    node[pos=0.65,above] {$c'_3$} ++ (agent1);

    \draw[double]
    (agent1) -- node[pos=0.15,above] {$a_1$} node[pos=0.85,above] {$a'_1$}
    node[pos=0.15,below] {$b_1$} node[pos=0.85,below] {$b'_1$} ++ (proc1);
    \draw[double]
    (agent2) -- node[pos=0.15,above] {$a_2$} node[pos=0.85,above] {$a'_2$}
    node[pos=0.15,below] {$b_2$} node[pos=0.85,below] {$b'_2$} ++ (proc2);
    \draw[double]
    (agent3) -- node[pos=0.15,above] {$a_3$} node[pos=0.85,above] {$a'_3$}
    node[pos=0.15,below] {$b_3$} node[pos=0.85,below] {$b'_3$} ++ (proc3);

>>>>

    \draw[->]
    (agent1) -- node[pos=0.35,above] {$c_1$}
    node[pos=1.0,above] {$c'_1$} ++ (agent2);
    \draw[->]
    (agent2) -- node[pos=0.1,above] {$c_2$}
    node[pos=0.9,above] {$c'_2$} ++ (agent3);
    \draw[->]
    (agent3) -- node[pos=0.0,above] {$c_3$}
    node[pos=0.65,above] {$c'_3$} ++ (agent1);

    \draw[implies-implies,double]
    (agent1) -- node[pos=0.15,above] {$a_1$} node[pos=0.85,above] {$a'_1$}
    node[pos=0.15,below] {$b_1$} node[pos=0.85,below] {$b'_1$} ++ (proc1);
    \draw[implies-implies,double]
    (agent2) -- node[pos=0.15,above] {$a_2$} node[pos=0.85,above] {$a'_2$}
    node[pos=0.15,below] {$b_2$} node[pos=0.85,below] {$b'_2$} ++ (proc2);
    \draw[implies-implies,double]
    (agent3) -- node[pos=0.15,above] {$a_3$} node[pos=0.85,above] {$a'_3$}
    node[pos=0.15,below] {$b_3$} node[pos=0.85,below] {$b'_3$} ++ (proc3);
